---
title: "ELOfootball"
author: "Manuel Fontenla Cadavid"
date: "28 de septiembre de 2015"
output: ioslides_presentation
---

## ELOfootball application

This application uses a simple implementation of the World Football Elo Rating System to rank the teams of the Premier League, from season 2000/2001 to 2015/2016, and compute the expectancies for two selected teams in a given match.

## Predict results

The user could select a home team and an away team and see its ELO ratings compared and the computed probabilities for each possible result of a match between them:

* "H": Home Win
* "D": Draw
* "H": Away Win

## Example

```{r, echo = FALSE}
# Load data
load("data/E0/updated.rda")
load("data/E0/ranking.rda")
load("data/E0/teams.rda")
source("R/ELOgame.R")
source("R/ELOpredict.R")
source("R/ELOranking.R")
source("R/ELOrating.R")
```
```{r}
ELOpredict(ranking, "Arsenal", "Chelsea", draw.prob = 0.2)
```

## More about ELO and data sources

You could learn more about the World Football Elo Rating System in [ELOratings.net](http://eloratings.net) or in its [Wikipedia page](https://en.wikipedia.org/wiki/World_Football_Elo_Ratings).

Results and data from previous matchs was obtained from [football-data.co.uk](football-data.co.uk).

## Live Demo

https://optrees.shinyapps.io/ELOfootball

